\thema

### 2019-09-10 Docs/paper/report.tex
use scaled image

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{../pics/ROC-curve}
\caption{To show the performance you can take a lock at the ROC. The calculated AUC is close to 96\%, wich means, that the model has a good class separation.}
\end{figure}

\section*{Conclusion and Future Work}
In summary, this paper argued that short term precipitation prediction can be done by only observing radar data and without any other source of information.
The accuracy could still be imporved as well at the regression, were another lossfunction may could help, as at the classification were the rainfall class is still undersampled and worse accurate than the 'no rain' class.

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{../pics/roc-curve-RESIZED_TXT}
\caption{The ROC shows the performance by classification. The calculated AUC is close to 97\%, wich means, that the model has a good class separation.}
\end{figure}

\section*{Conclusion and Future Work}
In summary, this paper argued that short term precipitation prediction can be done by only observing radar data and without any other source of information.
The accuracy could still be imporved as well at the regression, were another lossfunction may could help, as at the classification were the 'rainfall' class is still undersampled and worse accurate than the 'no rain' class.
